Almost compatible functions and infinite length games

### 2016-09-08 articles/almost-compatible-functions-and-topological-games/article.tex
many many revisions to address the referee's concerns

\usepackage{tikz}
\usetikzlibrary{matrix}

@@

\author{Steven Clontz}
\address{Department of Mathematics and Statistics, UNC Charlotte,
Charlotte, NC 28262}
\email{steven.clontz@gmail.com}
\author{Alan Dow}
\address{Department of Mathematics and Statistics, UNC Charlotte,
Charlotte, NC 28262}
\email{adow@uncc.edu}

@@

  \begin{definition}
    The statement \(\alcompS\kappa\) (given as \(S(\kappa,\aleph_0,\omega)\)
    in \cite{MR1129143} and \(S(\kappa)\) in \cite{clontzMengerGamePreprint})
    claims that there exist one-to-one functions
    \(f_A:A\to\omega\) for each \(A\in[\kappa]^{\leq\aleph_0}\) such that
    the collection \(\{f_A:A\in[\kappa]^{\leq\aleph_0}\}\) is pairwise
    almost compatible.
  \end{definition}

  In the same paper, Scheepers noted that \(\alcompS{\omega_1}\) holds in \(ZFC\),
  and that it's possible to force \(\mf c\) to be arbitrarily large
  while preserving \(\alcompS{\mf c}\). However, \(\alcompS{\mf c^+}\) always fails.
  This axiom may be applied to obtain a winning \(2\)-tactic for \(\pl F\)
  in the countable-finite game.

@@

  In the next section we will show that \(\alcompSP{\kappa}\) is sufficient
  for the applications to the Scheepers and Menger games.
  In the meantime, we will demonstrate that \(\alcompSP{\kappa}\) is strictly
  weaker than \(\alcompS{\kappa}\).

@@

  We now construct a topology on \(\omega_n\) for each \(n<\omega\) which
  will witness a Kurepa family of size \(\aleph_n\). A similar construction
  was previously shown by Juh\'asz et. al. in \cite{MR539228},
  and the relationship of
  Kurepa families and such spaces has also been investigated in a preprint
  of Nyikos \cite{NYIKOSKUREPA}.

  \begin{proposition}
    Let \(X\) be a \(T_2\) space with a base of countable and compact
    neighborhoods. Then \(X\) is locally metrizable with
    a base of compact open countable sets.
  \end{proposition}

  \begin{proof}
    For each point \(x\) let \(K\) be a countable and compact neighborhood
    of \(x\), and it follows that it is contained in a countable, open,
    and locally compact neighborhood \(W\) of \(x\), which in turn
    is zero-dimensional and metrizable. So choose \(V\) clopen
    in \(W\) such that \(x\in V\subseteq K\); \(V\) is a compact open
    neighborhood of \(x\) in \(X\).
  \end{proof}

@@

  \begin{proposition}
    Let \(X\) be a \(T_2\) space with cardinality less than \(\aleph_\omega\)
    which is locally countable and
    \(\omega\)-bounded. Then the closure operation preserves cardinality and
    weight.
  \end{proposition}

  \begin{proof}
    Note that the closure of any countable neighborhood is compact, and
    any Lindel\"of set is countable. This space is locally metrizable
    and thus first-countable, so cardinality and weight coincide for any
    subspace. The result is obvious if \(A\) is countable; otherwise
    let \(A=\{a_\alpha:\alpha<\omega_{n+1}\}\) and since basic neighborhoods
    are countable note any limit point of \(A\) is
    a limit point of \(A_\beta=\{a_\alpha:\alpha<\beta\}\)
    for some \(\beta<\omega_{n+1}\).
    Thus \(\cl A=\bigcup_{\beta<\omega_{n+1}}\cl{A_\beta}\) and
    by induction \(|\cl A|=|A|\).
  \end{proof}

  \begin{lemma}
    Let \(X\) be a \(T_2\) space with cardinality less than \(\aleph_\omega\)
    which is locally countable and locally compact, and such that
    its closure operation preserves cardinalities.
    Then \(X\) has an \(\omega\)-bounded extension \(\tilde X\)
    with the same properties where \(\tilde X\setminus X\) has the same
    cardinality as \(X\).
  \end{lemma}

  \begin{proof}
    We prove this by induction on \(n\).
    If \(n=0\), then we can just use the one-point compactification of two
    copies of \(X\). So suppose \(n>0\) and
    that \(X=\omega_n\) has an appropriate topology. Note that \(X\) has
    a base of countable and compact neighborhoods since the closure operation
    preserves cardinalities.

    For each \(\alpha<\omega_n\), \(\gamma_\alpha\) may be chosen such that
    both the closure of the set \(\alpha\) in \(X\) and a countable
    neighborhood of the point \(\alpha\) are subsets of \(\gamma_\alpha\).
    Note that the set
    \(\{\lambda<\omega_n:\alpha<\lambda\Rightarrow\gamma_\alpha<\lambda\}\)
    is a cub subset of \(\omega_n\) containing a cub subset \(C\)
    of limit ordinals.
    Now for each \(\lambda\in C\), the set \(\lambda\) is
    open as \(\alpha<\lambda\) belongs to the neighborhood
    \(\gamma_\alpha\subsetneq\lambda\). Also, if \(\lambda\) has uncountable
    cofinality, then for \(\beta\geq\lambda\) and any countable neighborhood
    \(U\) of \(\beta\), \(U\cap\lambda=U\cap\alpha\)
    for some \(\alpha<\lambda\); thus \(U\setminus\cl\alpha=U\setminus\lambda\)
    is a neighborhood of \(\beta\), showing that \(\lambda\)
    is clopen.

    Let \(\tilde X=\omega_n\times 2\).
    By induction on \(\lambda \in C\) we will define compatible topologies
    for \(\tilde X_\lambda=\omega_n\times\{0\}\cup\lambda\times\{1\}\)
    such that
    \begin{itemize}
      \item \(\omega_n \times \{0\}\) is an open copy of \(X\),
      \item \(\lambda\times 2\) is open, and when \(\cf\lambda>\omega\) also closed,
      \item the space has a base of countable and compact neighborhoods, and
      \item when \(\lambda\) is a successor,
        for each \(\alpha<\lambda\) the closure of \(\alpha\times 2\) is
        an \(\omega\)-bounded  subset of \(\lambda\times 2\).
    \end{itemize}

    We first consider the case \(n=1\).
    If \(\lambda\) is a limit in \(C\), then
    \(
      \tilde X_\lambda
        =
      \bigcup_{\mu\in C\cap\lambda}\tilde X_\mu
    \)
    satisfies the induction requirements.
    Otherwise we choose an increasing sequence of
    ordinals \(\{\alpha_k : k\in \omega\}\) with limit \(\lambda\)
    such that \(\alpha_0\) is the predecessor of \(\lambda\) in \(C\),
    or \(\alpha_0=0\) if \(\lambda\) is the least element of \(C\).

    The subspace \(\cl\lambda\times\{0\}\cup\alpha_0\times2\) of \(X\)
    is countable and locally compact; therefore it is
    metrizable and zero-dimensional.
    So we may choose increasing sets \(U_k\) for \(k<\omega\) which are
    clopen in this topology and satisfy
    \[
      \cl{\alpha_k\times\{0\}\cup\alpha_0\times2}
        =
      \cl{\alpha_k}\times\{0\}\cup\alpha_0\times2
        \subseteq
      U_k
        \subseteq
      \lambda\times\{0\}\cup\alpha_0\times 2
    \]
    Note that \(U_k\) is also clopen in \(\tilde X_{\alpha_0}\) since it is
    closed in \(\cl\lambda\times\{0\}\cup\alpha_0\times2\) and open in
    \(\lambda\times\{0\}\cup\alpha_0\times 2\).

    We need only describe a base for the points
    \(\<\alpha,1\>\in(\lambda\setminus\alpha_0)\times\{1\}\).
    We do so by letting
    \(\<\alpha,1\>\) be isolated when \(\alpha\not\in\{\alpha_k:k<\omega\}\),
    and giving \(\<\alpha_k,1\>\) the open neighborhoods
    \((U_k\cup((\alpha_k+1)\times\{1\}))\setminus K\) for each compact
    subset \(K\) of \(U_k\cup(\alpha_k\times\{1\})\); that is,
    \(\<\alpha_k,1\>\) is the one point compactifying
    \(U_k\cup(\alpha_k\times\{1\})\).

    The first two requirements of our inductive hypothesis are obviously
    satsified. Note points in \(\lambda\times 2\) are covered by
    the compact countable neighborhood \(U_k\cup((\alpha_k+1)\times\{1\})\)
    for some \(k<\omega\), and for points in
    \((\omega_n\setminus\lambda)\times\{0\}\) we may use a compact
    countable neighborhood from \(X\).
    For the final requirement, note that for \(\alpha<\lambda\), we may
    choose \(\alpha<\alpha_k<\lambda\) and note that
    \(\alpha\times 2\) is contained in the compact
    subset \(U_k\cup((\alpha_k+1)\times\{1\})\) of \(\lambda\times2\).

    For the case \(n>1\), we may assume that the successors in \(C\)
    have uncountable cofinality.
    We again proceed by induction on \(\lambda\in C\).  Again when
    \(\lambda\) is a limit in \(C\),
    \(
      \tilde X_\lambda
        =
      \bigcup_{\mu\in C\cap\lambda}\tilde X_\mu
    \)
    satisfies the given
    requirements; in particular if \(\alpha<\lambda\), then
    \(\alpha<\mu<\lambda\) for some successor \(\mu\in C\) with uncountable
    cofinality. As such, the closure of \(\alpha\times2\) is
    an \(\omega\)-bounded subset of the clopen \(\mu\times 2\) and
    therefore also of \(\lambda\times 2\).
    In case \(\lambda\) is not a limit of \(C\), then \(\lambda\)
    has uncountable cofinality and a predecessor \(\mu\in C\).
    We therefore have that \(\lambda\times\{0\}\) is clopen
    in \(\omega_n\times \{0\}\). Since the cardinality of
    \(\lambda\times \{0\} \cup \mu\times 2\) is less than \(\aleph_n\),
    we may simply apply the induction hypothesis
    to choose an appropriate topology for \(\lambda\times 2\).

    As a result, \(\tilde X=\bigcup_{\lambda\in C}\tilde X_\lambda\)
    is
    \(\omega\)-bounded as any countable set is contained in some
    \(\alpha\times 2\) for \(\alpha<\lambda\in C\).
  \end{proof}

  \begin{theorem}
    For each \(k< \omega\), there is a \(T_2\), locally countable,
    \(\omega\)-bounded topology on \(\omega_k\). That is, \(\splendidS{\aleph_k}\)
    for all \(k<\omega\).
  \end{theorem}

  \begin{proof}
    Apply the previous lemma to \(\omega_n\) with the discrete topology.
  \end{proof}

@@

  Weakening to the continuum hypothesis, we see an obvious consequence.

  \begin{corollary}[\(CH\)]
    \(\alcompSP{\mf c^+}\), but \(\neg\alcompS{\mf c^+}\).
  \end{corollary}

  But \(CH\) is not required to have \(\alcompS{\aleph_2}\) fail.

@@

  \begin{figure}[ht]
\begin{center}
\begin{tikzpicture}
  \matrix (m) [matrix of math nodes,row sep=3em,column sep=1em,minimum width=2em]
  {
    &
    \pl F \kmarkwin2\menGame{\oneptlind\kappa} &
    \pl F \kmarkwin2\schFillIntGame\kappa \\

    \alcompSP\kappa \\

    &
    \pl F \kmarkwin2\schFillInitialGame\kappa &
    \pl F \kmarkwin2\schFillGame\kappa \\
  };
  \path[>=latex,->]
    (m-2-1) edge (m-1-2)
    (m-2-1) edge (m-3-2)
    (m-1-2) edge (m-3-2)
    (m-1-3) edge (m-3-3);
  \path[>=latex,<->]
    (m-1-2) edge (m-1-3)
    (m-3-2) edge (m-3-3);
\end{tikzpicture}
\end{center}
\caption{Diagram of Scheeper/Menger game implications with \(\alcompSP{\kappa}\)}
\label{GamesDiagram2}
\end{figure}

%   \begin{figure}[h]
% \begin{center}
% \begin{tikzpicture}
%   \matrix (m) [matrix of math nodes,row sep=3em,column sep=1em,minimum width=2em]
%   {
%     &
%     \pl F \kmarkwin2\menGame{\oneptlind\kappa} &
%     \pl F \kmarkwin2\schFillIntGame\kappa \\

%     \alcompSP\kappa &
%     \pl F \kmarkwin2\schFillInitialGame\kappa &
%     \pl F \kmarkwin2\schFillGame\kappa \\

%     &
%     &
%     \pl F \ktactwin2\schFillStrictGame\kappa \\
%   };
%   \path[>=latex,->]
%     (m-2-1) edge (m-1-2)
%     (m-2-1) edge (m-2-2)
%     (m-2-1) edge (m-3-3)
%     (m-1-2) edge (m-2-2)
%     (m-1-3) edge (m-2-3)
%     (m-3-3) edge (m-2-3);
%   \path[>=latex,<->]
%     (m-1-2) edge (m-1-3)
%     (m-2-2) edge (m-2-3);
% \end{tikzpicture}
% \end{center}
% \caption{Diagram of Scheeper/Menger game implications with \(\alcompSP{\kappa}\)}
% \label{GamesDiagram2}
% \end{figure}

  \begin{theorem}
    \(\alcompSP\kappa\) implies the game-theoretic conditions
    shown in Figure \ref{GamesDiagram2}.
  \end{theorem}

  \begin{proof}
    The weaker claim
    \(\alcompS\kappa\Rightarrow\pl F \kmarkwin2\schFillIntGame\kappa\)
    was proven in \cite{clontzMengerGamePreprint};
    however, the strategy
    only required that the \(f_A\) be pairwise almost-compatible and
    that preimages of finite sets in each \(f_A\)
    are finite, which is also possible assuming \(\alcompSP\kappa\).
    Note that the relationships amongst the games were all shown in
    \cite{clontzMengerGamePreprint}.
  \end{proof}

  We include the following proof from \cite{MR1129143} for the convenience
  of the reader.

  \begin{theorem}
    \(\alcompS\kappa\Rightarrow\pl F \ktactwin2\schFillStrictGame\kappa\)
  \end{theorem}

@@

    As a result,
    \[
      \sigma(\<A,B\>)
        =
      \{\alpha\in A:g_A(\alpha)\leq g_B(\alpha)\}
    \]
    is a legal \(2\)-tactic for \(\pl F\). Let \(C=\<C_0,C_1,\dots\>\) be
    a strictly increasing sequence of countable sets and
    \(\alpha\in C_n\). Noting that \(f_A\) is an injection and not
    just finite-to-one, \(0\leq g_{C_{n+m}}(\alpha)\) for all
    \(m<\omega\), and it follows that
    \(g_{C_{n+m}}(\alpha)\leq g_{C_{n+m+1}}(\alpha)\) for some \(m<\omega\).
    Therefore \(\alpha\in\sigma(\<C_{n+m},C_{n+m+1}\>)\).
  \end{proof}

  So it would seem that \(\alcompSP\kappa\) is sufficient only when
  considering Markov strategies. (Of course,
  \(\alcompSP\kappa\Rightarrow\pl F\kmarkwin2\schFillGame\kappa
  \Rightarrow\pl F\kmarkwin2\schFillStrictGame{\kappa}\).)
  We would like to demonstrate that \(\alcompSP\kappa\) is not
  necessary.

@@

  \begin{proof}
    The proof proceeds nearly identically to the previous proof: substitute
    \(\alpha\in C_0\) in place of \(\alpha\in\bigcap_{n<\omega}C_n\) and proceed.
  \end{proof}
    % Let \(\sigma_n\) be a winning \(2\)-mark for \(\pl F\) in
    % \(\schFillInitialGame{\omega_{\beta_n}}\). Define the \(2\)-mark \(\sigma\)
    % for \(\pl F\) in \(\schFillInitialGame{\omega_\alpha}\) as follows:
    % \[
    %   \sigma(\<C\>,0)
    %     =
    %   \sigma_0(\<C\cap\omega_{\beta_0}\>,0)
    % \]
    % \[
    %   \sigma(\<C,D\>,n+1)
    %     =
    %   \sigma_{n+1}(\<D\cap\omega_{\beta_{n+1}}\>,0)
    %     \cup
    %   \bigcup_{m\leq n}
    %   \sigma_m(\<C\cap\omega_{\beta_m},D\cap\omega_{\beta_m}\>,n-m+1)
    % \]

    % Let \(\<C_0,C_1,\dots\>\) be an attack by
    % \(\pl C\) in \(\schFillInitialGame{\omega_\alpha}\), and
    % \(\alpha\in C_0\).
    % Choose \(N<\omega\) with \(\alpha<\omega_{\beta_{N+1}}\). Consider the
    % attack
    % \(\<C_{N+1}\cap\omega_{\beta_{N+1}},C_{N+2}\cap\omega_{\beta_{N+1}},\dots\>\)
    % by \(\pl C\) in \(\schFillInitialGame{\omega_{\beta_{N+1}}}\). Since
    % \(\sigma_{N+1}\) is a winning strategy and
    % \(\alpha\in C_{N+1}\cap\omega_{\beta_{N+1}}\), either
    % \(\alpha\in\sigma_{N+1}(\<C_{N+1}\cap\omega_{\beta_{N+1}}\>,0)\) and thus
    % \(\alpha\in\sigma(\<C_N,C_{N+1}\>,N+1)\), or
    % \(
    %   \alpha
    %     \in
    %   \sigma_{N+1}(
    %     \<C_{N+M+1}\cap\omega_{\beta_{N+1}},C_{N+M+2}\cap\omega_{\beta_{N+1}}\>
    %     ,M+1
    %   )
    % \)
    % for some \(M<\omega\) and thus
    % \(
    %   \alpha
    %     \in
    %   \sigma(
    %     \<C_{N+M+1},C_{N+M+2}\>,
    %     N+M+2
    %   )
    % \). Thus \(\sigma\) is a winning strategy.

@@

  We conclude by returning our attention to Question \ref{mainQuestion},
  which asks whether there exists a space for which the second player
  \(\pl F\) in the Menger game \(\menGame{X}\) has a winning strategy
  without a winning \(2\)-mark.

@@

  Solving the following weaker question would not answer Question
  \ref{mainQuestion} by itself, but an solution would be interesting nonetheless.

@@

>>>>

\usepackage{tikz}
% \usetikzlibrary{matrix}
\usetikzlibrary{arrows}

@@

\author{Steven Clontz}
\address{Department of Mathematics and Statistics,
The University of South Alabama,
Mobile, AL 36606}
\email{steven.clontz@gmail.com}
\author{Alan Dow}
\address{Department of Mathematics and Statistics, UNC Charlotte,
Charlotte, NC 28262}
\email{adow@uncc.edu}

@@

  \begin{definition}
    The statement \(\alcompS\kappa\) (given as \(S(\kappa,\aleph_0,\omega)\)
    in \cite{MR1129143})
    claims that there exist one-to-one functions
    \(f_A:A\to\omega\) for each \(A\in[\kappa]^{\leq\aleph_0}\) such that
    the collection \(\{f_A:A\in[\kappa]^{\leq\aleph_0}\}\) is pairwise
    almost compatible.
  \end{definition}

  In \cite{MR1129143}, Scheepers noted that \(\alcompS{\omega_1}\) holds in \(ZFC\),
  and that it's possible to force \(\mf c\) to be arbitrarily large
  while preserving \(\alcompS{\mf c}\). However, \(\alcompS{\mf c^+}\) always fails.
  This axiom may be applied to obtain a winning \(2\)-tactic for \(\pl F\)
  in the countable-finite game.

@@

  In the final section we will show that \(\alcompSP{\kappa}\) is sufficient
  for many applications to the Scheepers and Menger games.
  In the meantime, we will demonstrate that \(\alcompSP{\kappa}\) is strictly
  weaker than \(\alcompS{\kappa}\).

@@

  We now construct a topology on \(\omega_n\) for each \(n<\omega\) which
  will witness a Kurepa family of size \(\aleph_n\), exploiting a theorem of
  Juh\'asz et. al. in \cite{MR539228}.

@@

  \begin{theorem}[\cite{MR539228}]
    \(\splendidS{\aleph_k}\) for \(k<\omega\).
  \end{theorem}

@@

  As noted earlier, Scheepers proved in \cite{MR1129143}
  that \(\neg\alcompS{\mf c^+}\) is a theorem of ZFC, showing
  \(\alcompSP{\kappa}\) is not equivalent to \(\alcompS{\kappa}\).

  We now demonstrate that \(CH\) is not required to have \(\alcompS{\aleph_2}\)
  fail.

@@

  \begin{figure}[ht]
\begin{center}
\begin{tikzpicture}[x=0.8in,y=0.5in]
  \node at (-3.5,2) {\(\alcompS\kappa\)};
  \node at (-3.5,0) {\(\pl F \ktactwin2\schFillStrictGame\kappa\)};
  \node at (0,2) {\(\alcompSP\kappa\)};
  \node at (-1,1) {\(\pl F \kmarkwin2\menGame{\oneptlind\kappa}\)};
  \node at (0,1) {\(\Leftrightarrow\)};
  \node at (1,1) {\(\pl F \kmarkwin2\schFillIntGame\kappa\)};
  \node at (-1,0) {\(\pl F \kmarkwin2\schFillInitialGame\kappa\)};
  \node at (0,0) {\(\Leftrightarrow\)};
  \node at (1,0) {\(\pl F \kmarkwin2\schFillGame\kappa\)};
  \node at (0,-1) {\(\pl F \kmarkwin2\schFillStrictGame\kappa\)};
  \draw[-implies,double equal sign distance] (-3.2,2) -- (-0.3,2);
  \draw[-implies,double equal sign distance] (-2.6,0) -- (-1.9,0);
  \draw[-implies,double equal sign distance] (-3.5,1.65) -- (-3.5,0.35);
  \draw[-implies,double equal sign distance] (0,1.65) -- (0,1.35);
  \draw[-implies,double equal sign distance] (0,0.65) -- (0,0.35);
  \draw[-implies,double equal sign distance] (0,-0.35) -- (0,-0.65);
\end{tikzpicture}
\end{center}
\caption{Diagram of Scheeper/Menger game implications with \(\alcompS{\kappa},\alcompS{\kappa}\)}
\label{GamesDiagram}
\end{figure}

  \begin{theorem}
    Figure \ref{GamesDiagram}.
  \end{theorem}

  \begin{proof}
    \(\alcompS\kappa\Rightarrow\pl F \ktactwin2\schFillStrictGame\kappa\) was
    shown by Scheepers in \cite{MR1129143} (also, see the following theorem).
    Most of the other results in the figure were proven
    in \cite{clontzMengerGamePreprint}, with the exception that
    \(\alcompSP\kappa\) was not considered at the time.
    The following proof that
    \(\alcompSP\kappa\Rightarrow\pl F \kmarkwin2\schFillIntGame\kappa\)
    is a trivial modification of the proof presented in
    \cite{clontzMengerGamePreprint} assuming \(\alcompS\kappa\), but as
    that paper is under review at the time
    of this writing, we provide it here.

    Let \(f_A\) for \(A\in[\kappa]^{\leq\omega}\) witness \(\alcompSP\kappa\).
    We define a \(2\)-mark \(\sigma\) for \(\schFillIntGame\kappa\) as follows:
      \[
        \sigma(\<A\>,0) = \{\alpha\in A: f_A(\alpha) = 0 \}
      \]
      \[
        \sigma(\<A,B\>,n+1)
          =
        \{
          \alpha \in A\cap B
        :
          f_B(\alpha) \leq n+1 \text{ or }
          f_A(\alpha)\not=f_B(\alpha)
        \}
      \]
    For any attack \(\<A_0,A_1,\dots\>\) by \(\pl C\) and
    \(\alpha\in\bigcap_{n<\omega}A_n\), either \(f_{A_n}(\alpha)\) is constant for
    all \(n\), or \(f_{A_n}(\alpha)\not=f_{A_{n+1}}(\alpha)\) for some \(n\);
    either way, \(\alpha\) is covered.
  \end{proof}

  We include the following proof from \cite{MR1129143} to point
  out why \(\alcompSP\kappa\) seems insufficient for providing \(\pl F\) a
  winning \(2\)-tactic in \(\schFillStrictGame\kappa\), despite that it
  witnesses a winning \(2\)-mark.

  \begin{theorem}[\cite{MR1129143}]
    \(\alcompS\kappa\Rightarrow\pl F \ktactwin2\schFillStrictGame\kappa\)
  \end{theorem}

@@

    As a result,
    \[
      \sigma(\<A,B\>)
        =
      \{\alpha\in A:g_A(\alpha)\leq g_B(\alpha)\}
    \]
    is a legal \(2\)-tactic for \(\pl F\). Let \(C=\<C_0,C_1,\dots\>\) be
    a strictly increasing sequence of countable sets and
    \(\alpha\in C_n\).

    Noting that \(f_A\) is an injection
    (not just finite-to-one), \(0\leq g_{C_{n+m}}(\alpha)\) for all
    \(m<\omega\), and it follows that
    \(g_{C_{n+m}}(\alpha)\leq g_{C_{n+m+1}}(\alpha)\) for some \(m<\omega\).
    Therefore \(\alpha\in\sigma(\<C_{n+m},C_{n+m+1}\>)\).
  \end{proof}

  While the above proof cannot be trivially modified to utilize
  the finite-to-one functions witnessed by
  \(\alcompSP\kappa\) in constructing a winning \(2\)-tactical strategy
  for \(\schFillStrictGame{\kappa}\), whether
  \(\alcompSP\kappa\) is sufficient for
  \(\pl F\ktactwin2\schFillStrictGame{\kappa}\) after all
  does remain open:

  \begin{question}
    May the previous theorem be improved by replacing \(\alcompS\kappa\)
    with \(\alcompSP\kappa\)?
  \end{question}

  We would like to demonstrate that \(\alcompSP\kappa\) is not
  necessary for constructing winning \(2\)-Markov strategies in
  \(\schFillIntGame\kappa\).

@@

  \begin{proof}
    The proof proceeds nearly identically to the previous proof: substitute
    \(\alpha\in C_0\) in place of \(\alpha\in\bigcap_{n<\omega}C_n\) and proceed.
  \end{proof}

@@

  We conclude by returning our attention to Question \ref{mainQuestion},
  which asks whether there exists a space for which the second player
  \(\pl F\) in the game \(\menGame{X}\) has a winning strategy
  without a winning \(2\)-mark.

@@

  Solving the following weaker question would not answer Question
  \ref{mainQuestion} by itself, but a solution would be interesting nonetheless.

@@

  Although, it's still open whether the previous two questions are even
  distinct.

  \begin{question}
    Can a winning \(2\)-Markov strategy in \(\schFillGame{\kappa}\)
    be used to construct a winning \(2\)-Markov strategy in
    \(\schFillIntGame{\kappa}\)?
  \end{question}
